My title

### 2024-06-26 paper/paper.qmd
downloading and cleaning scripts

```{r}
#| include: false
#| warning: false
#| message: false
#install.packages("usethis")
#install.packages("gitcreds")
library(usethis)
library(gitcreds)
create_github_token()

>>>>

```{r}
##| include: false
##| warning: false
##| message: false
#install.packages("usethis")
#install.packages("gitcreds")
#library(usethis)
#library(gitcreds)
#create_github_token()
# Example dataframe with values and ranges
data_ranges <- data.frame(
  category = c("A", "B", "C", "D"),
  value = c(100, 150, 200, 250),
  range = c(10, 15, 20, 25)  # Example range values
)

# Calculate upper and lower bounds for plotting
data_ranges$lower <- data_ranges$value - data_ranges$range
data_ranges$upper <- data_ranges$value + data_ranges$range

# Print the dataframe
print("Data with Ranges:")
print(data_ranges)
# Load necessary library
library(ggplot2)

# Create the plot
ggplot(data_ranges, aes(x = category, y = value)) +
  geom_point() +  # Plot points for values
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +  # Error bars for ranges
  labs(title = "Values with Ranges", x = "Category", y = "Value") +
  theme_minimal()
